\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Test 5}
  \\ \vspace{1em}
  \textbf{\large April Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $4\frac{1}{2}$ hours}
\end{center}

\vfill

\begin{enumerate}[leftmargin=0pt, itemsep=18pt]

\item
An infinite number of hunters and rabbits are engaged in thermo-nuclear war on the coordinate plane. Each hunter and each rabbit occupies a point on the plane with integer coordinates, with no two agents occupying the same point. 

Each hunter has a North Star™ Powered Thermal Disintegrator. If this device is at the point $(m, n)$, then any biological lifeform (hunter or rabbit) on either the points $(m - 1, n + 1)$ and $(m + 1, n + 1)$ is instantly destroyed.

Each rabbit has a Southern Cross™ Active Meson Blaster. If this device is at the point $(m, n)$, then any organism (hunter or rabbit) unlucky enough to be on the point $(m - 1, n - 1)$ or on the point $(m + 1, n - 1)$ rapidly perishes.

Suppose that we have a $m \times n$ grid of lattice points. What is the maximum number of hunters and rabbits (in total) that can occupy these points in such a way that no one is involved in an unfortunate weapons mishap?


\item % IMOSL 2020 A3
Suppose that $a$, $b$, $c$, and $d$ are positive real numbers satisfying $(a+c) (b+d) = ac +bd$.
Find the smallest possible value of
\[ \frac{a}{b} +\frac{b}{c} +\frac{c}{d} +\frac{d}{a}. \]


\item % IMOSL 2020 G5
Let $ABCD$ be a cyclic quadrilateral with no two sides parallel.
Let $K$, $L$, $M$, and $N$ be points lying on segments $AB$, $BC$, $CD$, and $DA$ respectively such that $KLMN$ is a rhombus with $KL \parallel AC$ and $LM \parallel BD$.
Let $\omega_1$, $\omega_2$, $\omega_3$, and $\omega_4$ be the incircles of triangles $ANK$, $BKL$, $CLM$, and $DMN$ respectively.
Prove that the internal common tangents to $\omega_1$ and $\omega_3$ and the internal common tangents to $\omega_2$ and $\omega_4$ are concurrent.

\end{enumerate}


\vfill
\vfill
\begin{itemize}
	\item Submit your solutions at \url{https://forms.gle/uhMSLew7qTQ9Qbqr6}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\scriptsize
\begin{BVerbatim}
      _______
     / _   _ \
    / (.) (.) \
   ( _________ )
    \`-V-|-V-'/
     \   |   /
      \  ^  /
       \    \
        \    `-_
         `-_    -_
            -_    -_
Max         _-    _-
          _-    _-
        _-    _-
      _-    _-
      -_    -_
        -_    -_
          -_    -_
            -_    -_
            _-    _-
  ,-=:_-_-_-_ _ _-_-_-_:=-.
 /=I=I=I=I=I=I=I=I=I=I=I=I=\
|=I=I=I=I=I=I=I=I=I=I=I=I=I=|
|I=I=I=I=I=I=I=I=I=I=I=I=I=I|
\=I=I=I=I=I=I=I=I=I=I=I=I=I=/
 \=I=I=I=I=I=I=I=I=I=I=I=I=/
  \=I=I=I=I=I=I=I=I=I=I=I=/
   \=I=I=I=I=I=I=I=I=I=I=/
    \=I=I=I=I=I=I=I=I=I=/
     `================='
\end{BVerbatim}

\end{document}
