\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{booktabs}

\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 4 Solutions}
  % LEVEL is Senior, Intermediate or Beginner
  % NUMBER is the test number: 1, 2, etc.
  \\ \vspace{1em}
  \textbf{\large January Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\vspace{24pt}

\begin{enumerate}[1.]

\item % Tim
{\itshape Find all functions $f : \mathbb{R} \to \mathbb{R}$ such that for all $x, y \in \mathbb{R}$ we have that
\[ xf(y) = yf(x). \]}

Let $y = 1$ $$xf(1) = f(x)$$ If we let $m = f(1)$, we see that the solution is just $f(x) = mx$ for $m \in \mathbb{R}$.

Check for $f(x) = mx$:$$LHS = xf(y) = xmy = mxy$$ $$RHS = yf(x) = ymx = mxy$$ $LHS = RHS$, so the function checks.

\item % Croatia 2017 2nd round 3.2
{\itshape Find all positive integers $m$ such that $2^{m^2}-4$ is divisible by $7$.}

We want to find $m$ such that $2^{m^2}\equiv _{7} 4$. 
The possible remainders when $2^k$ is divided by 7 where $k$ is a natural number will be as follows:
\begin{align*} 
2^1 = 2 \equiv _{7} 2\\
2^2 = 4 \equiv _{7} 4\\
2^3 = 8 \equiv _{7} 1\\
2^4 = 16 \equiv _{7} 2\\
2^5 = 32 \equiv _{7} 4\\
2^6 = 64 \equiv _{7} 1
\end{align*}
This pattern will continue and we will see that $2^k$ mod 7 will be one of 1, 2, or 4. 
We also note that $2^k \equiv _{7} 4$ when $k \equiv _{3} 2$. 
If $k = m^2$ we have that $m^2 \equiv _{3} 2$. The possible remainders for when $m^2$ is divided by 3 will as follows:
\begin{align*}
1^2 = 1 \equiv _{3}  1 \\
2^2 = 4 \equiv _{3}  1 \\
3^2 = 9 \equiv _{3}  0 \\ 
4^2 = 16 \equiv _{3}  1 \\
5^2 = 25 \equiv _{3}  1 \\ 
6^2 = 36 \equiv _{3}  0
\end{align*}
This pattern will continue and we will see that $m^2$ mod 3 will be 0 or 1.
This means that a perfect square cannot leave a remainder of 2 when divided by 3, and thus there are no solutions for m.

\item % Croatia 2017 2nd round 2.4
{\itshape Consider a triangle $ABC$ with circumcentre $O$.
The angle bisector of $\angle BAC$ meets the opposite side $BC$ at $D$, and the altitude from $B$ onto $AD$ intersects line $AO$ at $E$.
Show that $A$, $B$, $D$, and $E$ are concyclic.}

Let the angle bisector of $A$ intersect the perpendicular bisector of $BC$ in point $S$, which is on the circumcircle of the triangle. Then $\angle EAD = \angle OAS = \angle OSA = \angle OSD = \angle EBD$. Hence $ABDE$ is cyclic.



\item % Tim
{\itshape Consider a $3\times3\times3$ 3-dimensional chess cube with some hyperrooks.
Hyperrooks can move along any direction parallel to an edge of the cube (like a normal rook, but also up and down).
What is the maximum number of hyperrooks you can place in the chess cube without any of them attacking each other?}

First, we prove that 9 hyperrooks is the maximum amount of hyperrooks you can place on a chess cube. Consider the 9 columns (in the up-down direction) of the chess cube. If a column contains 2 hyperrooks, the hyperrooks would attack each other. Therefore, each column has at most 1 hyperrook. Since there are 9 columns, there are at most 9 hyperrooks. We show that placing 9 hyperrooks is possible by construction.

Construction for 9 rooks:
\begin{table}[h]
\centering
\begin{tabular}{| c | c| c |}
\multicolumn{3}{c}{Top layer}\\
\hline
R& &\\
\hline
&R&\\
\hline
&&R\\
\hline
\end{tabular}
\quad
\begin{tabular}{| c | c| c |}
\multicolumn{3}{c}{Middle layer}\\
\hline
&R &\\
\hline
&&R\\
\hline
R&&\\
\hline
\end{tabular}
\quad
\begin{tabular}{| c | c| c |}
\multicolumn{3}{c}{Bottom layer}\\
\hline
& &R\\
\hline
R&&\\
\hline
&R&\\
\hline
\end{tabular}
\end{table}

\item % Sharp Maths Competition, Easter Egg for Liam
{\itshape Find all positive integers $a$, $b$ and $c$ satisfying 
$$a + b - c = 14$$
$$a^2 + b^2 - c^2 = 14.$$}

Rearranging the first equation, we have $c = a + b - 14$. We can substitute this into the second equation to get 
\begin{align*}
  a^2 + b^2 - c^2 &= 14 \\
  \implies a^2 + b^2 - (a + b - 14)^2 &= 14 \\
  \implies -2ab + 28a + 28b - 196 &= 14 \\
  \implies ab - 14a - 14 b + 98 &= -7 \\
  \implies (a - 14)(b - 14) - 98 &= -7 \\
  \implies (a - 14)(b - 14) &= 91 = 7 \cdot 13
\end{align*}
If $a$ and $b$ are integers, then so are $a - 14$ and $b - 14$. So we have that $a - 14$ and $b - 14$ must simply be the paired factors of $91$. We can not check every case 
\begin{align*}
  (a - 14, b - 14) &= (91, 1) \implies (a, b) = (105, 15) \\
  &= (13, 7) \implies (a, b) = (27, 21) \\
  &= (-13, -7) \implies (a, b) = (1, 7) \\
  &= (-91, -1) \implies (a, b) = (-77, 13)
\end{align*}
Notice that swapping $a$ and $b$ will produce more solutions which are just the same as the ones already generated, but also swapped. If we know $a$ and $b$, we can find $c$. Hence, using the condition that $a$, $b$, $c \in \mathbb{N}$, the only solutions are
\begin{align*}
  (a, b, c) &= (105, 15, 106) \\
  &= (27, 21, 34) \\
\end{align*}
where $a$ and $b$ may also be swapped in each triple.

\end{enumerate}

\vfill
% ASCII art
\centering
\tiny
\begin{BVerbatim}
       ,----,
  ___.`      `,
  `===  D     :
    `'.      .'
       )    (                   ,
      /      \_________________/|
     /                          |
    |                           ;
    |               _____       /
    |      \       ______7    ,'
    |       \    ______7     /
     \       `-,____7      ,'   
^~^~^~^`\                  /~^~^~^~^
 ~^~^~^ `----------------' ~^~^~^
~^~^~^~^~^^~^~^~^~^~^~^~^~^~^~^~
\end{BVerbatim}
\end{document}
