\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 5}
  \\ \vspace{1em}
  \textbf{\large January Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $4$ hours}
\end{center}

\vspace{12pt}

\begin{enumerate}[1.]

\item % Tim
A square-based pyramid has all of its edges the same length.
A cube is placed inside so that one of its faces lies on the base of the pyramid, and the opposite face has an edge along each side of the pyramid (think -- the natural way to put a cube in a pyramid).
Show that the sum of any of the cube's edge lengths with any of the cube's face diagonal lengths is the same as the edge length of the pyramid.


\item % Ireland 2017 Q15
There is a soccer competition with five teams where each team plays exactly one match against each other team.
If one team wins against another team, that team gets $5$ points whereas the losing team gets $0$ points.
If two teams draw, they each get $1$ point if neither team scored a goal and they each get $2$ points if they scored at least one goal.
At the end of the competition it is found that the total points for the teams form five consecutive nonnegative integers.
What is the minimum number of goals scored in this competition?


\item % Norwegian MO 1998, P1
Given a sequence $a_0$, $a_1$, $a_2$, $\cdots$, of natural numbers with $a_0 = 1$ and $a_{n}^2 > a_{n - 1}a_{n + 1}$ for all $n > 0$, show that 
\begin{enumerate}[a)]
  \item $a_n < a_1^n$ for all $n > 1$.
  \item $a_n > n$ for all $n$.
\end{enumerate}


\item % ELMO 2013 Shortlist, C8
There are $20$ people at a party. Each person holds some number of coins. Every minute, each person who has at least $19$ coins simultaneously gives one coin to every other person at the party. What is the smallest number of coins that could be at the party such that at least one coin is given out in every minute? 


\item % 
Given a function $f: \mathbb{Q} \rightarrow \mathbb{Q}$ satisfying
\begin{enumerate}[i)]
  \item $f(0) = 2$ and $f(1) = 3$
  \item For all rational numbers $x$ and all integers $n$, we have 
  $$f(x + n) - f(x) = n(f(x + 1) - f(x)) $$
  \item For all non-zero rational numbers $x$, we have $f(x) = f(\frac{1}{x})$
\end{enumerate}
Find all possible rational values of $x$ such that $f(x) = 2021$.


\item % Turkic TST 2008, Q1
Let $\triangle ABC$ have $ \angle B > \angle C$.
The internal angle bisector of $A$ intersects $BC$ at $D$ and the external angle bisector of $A$ intersect $BC$ at $E$.
$P$ is a variable point on $EA$ such that $A$ lies on the segment $EP$.
$DP$ intersects $AC$ at $M$ and $ME$ intersects $AD$ at $Q$.
Prove that all lines $PQ$ intersect at a unique point as $P$ changes.

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \url{https://forms.gle/M1L9KgbwzDxCKEjD9}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\clearpage
~
\vfill
% ASCII art
\centering
% \tiny
\begin{BVerbatim}
                                                      ____
                                                     /    `.
                                                    /-----.|          ____
                                                ___/___.---`--.__.---'    `--.
                                  _______.-----'           __.--'             )
                              ,--'---.______________..----'(  __         __.-'
                                        `---.___,-.|(a (a) /-'  )___.---'
                                                `-.>------<__.-'
            ______                       _____..--'      //
    __.----'      `---._                `._.--._______.-'/))
,--'---.__              -_                  _.-(`-.____.'// \
          `-._            `---.________.---'    >\      /<   \
              \_             `--.___            \ \-__-/ /    \
                \_                  `----._______\ \  / /__    \
                  \                      /  |,-------'-'\  `-.__\
                   \                    (   ||            \      )
                    `\                   \  ||            /\    /
                      \                   >-||  @)    @) /\    /
                      \                  ((_||           \ \_.'|
                       \                    ||            `-'  |
                       \                    ||             /   |
                        \                   ||            (   '|
                        \                   ||  @)     @)  \   |
                         \                  ||              \  )
                          `\_               `|__         ____\ |
                             \_               | ``----'''     \|
                               \_              \    .--___    |)
                                 `-.__          \   |     \   |
                                      `----.___  \^/|      \/\|
                                               `--\ \-._  / | |   (FL)
                                                   \ \  `'  \ \
                                            __...--'  )     (  `-._
                                           (_        /       `.    `-.__
                                             `--.__.'          `.       )
                                                                 `.__.-'
\end{BVerbatim}
\vfill

\end{document}
