\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 2}
  % LEVEL is Senior, Intermediate or Beginner
  % NUMBER is the test number: 1, 2, etc.
  \\ \vspace{1em}
  \textbf{\large January Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\vspace{24pt}

\begin{enumerate}[1.]

\item % Taariq, well known, not even a problem really
Let $\triangle ABC$ be an isosceles triangle with $AB = BC$. Let $H$ be the orthocentre of $\triangle ABC$ and let $K$ be the reflection of $H$ across $BC$. Prove that $HBKC$ is a parallelogram.


\item % Taariq, modified from AIME
Let $a$ and $r$ be real numbers such that
\[ a +ar +ar^2 +ar^3 +\dotsb +ar^{2020} = 200 \qquad\text{and}\qquad a +ar +ar^2 +ar^3 +\dotsb +ar^{4041} = 380. \]
Find the value of
\[ a +ar +ar^2 +ar^3 +\dotsb +ar^{6062}. \]


\item % Jon
Isaac is planning a nine-day holiday. Every day he will go surfing, or water skiing, or he will rest. On any given day he does just one of these three things. He never does different water-sports on consecutive days. How many schedules are possible for the holiday?

\item % Danielle from Ukrainian MO
A positive integer $N$ has exactly $2021$ positive divisors (including $1$ and $N$ itself), and it is divisible by $2021$.
Prove that $N$ is not divisible by $2021^{43}$.


\item % Ralph: found in one of the books. Can't remember which one.
Let $a$, $b$, $c$, $x$, $y$ and $z$ be positive real numbers with $a + b + c = x + y + z$.
Prove that 
\[ \frac{a}{x + y} + \frac{b}{y + z} + \frac{c}{z + x} + \frac{x}{a + b} + \frac{y}{b + c} + \frac{z}{c + a} > 2. \]


\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \url{https://forms.gle/QiVwLteHxnQSUF9y7}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\begin{BVerbatim}
\end{BVerbatim}

\end{document}
