\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced February Monthly Assignment}
  \\ \vspace{1em}
  \textbf{\large Due date: 20 February 2021}
\end{center}

\vspace{12pt}

\begin{enumerate}[1.]

\vspace{24pt}
\item % Danielle/Taariq
Let $c$ and $d$ be positive divisors of a natural number $n$ such that $c > d$. Prove that $$c > d + \frac{d^2}{n}.$$


\vspace{24pt}
\item % Ireland 2018 Q9
Suppose $a,b,c > 0$ and $\sqrt{a-b} +\sqrt{a-c} > \sqrt{b+c}$. Prove that $a > \dfrac{3}{4} (b+c)$.


\vspace{24pt}
\item % NH-2006-1
Let $ABCD$ be a square.
Points $P$ and $Q$ lie on the segments $AD$ and $DC$ such that $\angle PBQ = 45^\circ$.
Prove that $BP$ bisects $\angle APQ$ and $BQ$ bisects $\angle AQP$.


\vspace{24pt}
\item % French Number Theory Training Assignment
Let $n$ be a positive integer. Show that there is a positive integer $m$ such that $\varphi(m) = n!$, where $\varphi$ denotes the Euler phi function.


\vspace{24pt}
\item % China North MO 2020 Advanced Level P1
Define the function $f(x) = x^2 + \sin(x)$ (where $x$ is in radians in this context). Furthermore, let $\{a_n\}$ be a sequence with $a_n \in \mathbb{R}^+$ for all $n \in \mathbb{N}$. Let $a_1 = 1$, and $f(a_n) = a_{n - 1}$ for $n \ge 2$. Prove that there exists $n \in \mathbb{N}$ such that 
$$\sum_{k = 1}^n a_i > 2021.$$


\vspace{24pt}
\item % Ukraine 2016-2017 p54 Q10
Consider a triangle $ABC$ with points $M$ and $N$ on $BC$ and $AB$ respectively such that $AM \perp BC$ and $CN \perp AB$, and let $AC$ and $MN$ intersect at $Y$.
Let $X$ be a point inside triangle $ABC$ such that $MBNX$ is a parallelogram.
Prove that the angle bisectors of $\angle MXN$ and $\angle MYC$ are perpendicular.


\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \url{https://forms.gle/yoD4U3zZxs2yuP4d9}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\end{document}
