\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate March Monthly Assignment}
  \\ \vspace{1em}
  \textbf{\large Due date: 31 March 2021}
\end{center}

\vfill
\vfill

\begin{enumerate}[1.]

\vfill
\item % Tim Schlesinger, probably exists in the public domain
Two players play a game on a ${4\times n}$ checkerboard. They take turns to place checkers according to the following rule: no checker can be on a square that is adjacent (by either edge or vertex) to a square that already contains a checker. The last player to place a checker wins. Show that Player 2 can always win such a game.


\vfill
\item % Tim Schlesinger, probably well-known
We are given ${\Delta ABC}$. Lines ${l_B}$ and ${l_C}$ are the external angle bisectors at ${B}$ and ${C}$ respectively. ${p_1}$ is the perpendicular line from ${B}$ to ${l_C}$ and ${p_2}$ from ${C}$ to ${l_B}$. ${A'}$ is the intersection of lines ${p_1}$ and ${p_2}$. ${B'}$ and ${C'}$ are defined analogously (as the intersection of \textit{the perpendicular from one vertex of the triangle to the external angle bisector of another vertex} with \textit{the perpendicular from the second vertex to the external angle bisector of the original vertex}). Show that the area of hexagon ${AB'CA'BC'}$ is twice the area of ${\Delta ABC}$.


\vfill
\item % Tim Schlesinger
Solve for positive integers a,b,c:
\begin{align*}
a^2+bc&=181\\
ab+ac&=820
\end{align*}


\vfill
\item % Must be algebra


\vfill
\item % Tim Schlesinger, definitely standard graph theory stuff
There are $n$ towns in a country.
Every road in this country goes from one of these towns to another.
Two independent routes from town $A$ to town $B$ are routes that do not both go through any other town $C$.
If we are told that there are at least two independent routes from any town $A$ to any other town $B$, what is the minimum number of roads that could be in this country?


\vfill
\item % Tim Schlesinger
Let $ABC$ be a triangle with centroid $G$.
$\Gamma$ is the circle with diameter $BG$ and $H$ is its centre.
Let $CG$ extended intersect $AB$ at $F$ and $\Gamma$ at $I$ different to $G$.
Let $AG$ extended intersect $BC$ at $D$ and $\Gamma$ at $J$ different to $G$. Show that $IJ$ is parallel to $FD$ if and only if $I$, $H$, and $J$ are collinear.

\end{enumerate}


\vfill
\vfill

\begin{itemize}
	\item Submit your solutions at \url{https://forms.gle/Kx1QDxDT5xP3Ez547}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\end{document}
